---
title: "NARC-2"
format: html
---

## Overview

NARC 2 is the second HF station on your left as you enter the station.

### Equipment summary

- FlexRadio Flex 6400M (HF + 6m) transceiver
    - Astron RS-35A power supply
- Clipper PTT footswitch

- Dell PC, dual monitor set-up

- Elecraft KPA1500 amplifier
  - Elecraft power supply
  
### Connection scheme

```{mermaid}
flowchart TD
  A[Flex 6400M] ---|Coax-Ant1|B[KPA-1500 Ant 1]
  B ---|50A PowerPole|T[Elecraft Power Supply]
  T ---|220V AC|U(220V outlet)
  J ---|120V AC|V(110V outlet)
  A ---|Cat 6|L
  A ---|Tx1 RCA Rem|B
  A --> N(Clipper footswitch)
  A ---|RCA|Q(Relay)
  Q --- R(Kasa Switch)
  R --- J
  A ---|USB|C[NARC2 PC]
  C ---|USB|F(Keyboard)
  C ---|Bluetooth|G(Mouse)
  C ---|HDMI|H(Monitor)
  C ---|CAT 6|L(Network Switch)
  C ---|USB|P(FlexControl Knob)
  J ---|AC Power|C
  E ---|120V AC|I(Kasa Switch)
  I ---|AC Power|J[Surge Protector]
  I ---|Wifi|K(NARC wifi)
  A ---|Power Cable|E[Astron RS-35A]
  B ---|Coax Ant1|D(Antenna Connectors)
  H ---|AC Power|J
```
   
 
### Software summary

- Windows 10
- Digital modes
  - WSTJ-X
  - JS8Call
  - fldigi suite
  - VarAC
- Logging
  - N1MM
  - Amateur Contact Log (ACLog) by N3FJP

```{r}
#| include: false
library(knitr)
```

```{r}
#| echo: false
#| results: asis
#| 
a <- knitr::knit_child('flex-6400M.qmd', quiet=T)
cat(a, sep="\n")
```
