---
title: "Software"
format: html
---

::: {.callout-note}

These sections are generated by parsing a CSV data file in `include/csv/software_versions.csv`.

The code is hidden in the output for aesthetic reasons, but may be revealed by examining the source code file.

:::

```{r}
#| echo: false
software_versions <- readr::read_csv("include/csv/software_versions.csv", show_col_types = FALSE)
```

## Operating System

```{r}
#| echo: false
software_versions |>
  dplyr::filter(type == "os") |>
  dplyr::select(station,software, version, date) |>
  knitr::kable(format = "html") 
```

## Digital modes

```{r}
#| echo: false
software_versions |>
  dplyr::filter(type == "digital") |>
  dplyr::select(station,software, version, date) |>
  dplyr::arrange(software) |>
  knitr::kable(format = "html") 
```

## Logging

```{r}
#| echo: false
software_versions |>
  dplyr::filter(type == "logging") |>
  dplyr::select(station,software, version, date) |>
  dplyr::arrange(software) |>
  knitr::kable(format = "html") 
```

See the separate chapter on [logging](logging.qmd) for details about how to interface digital logging programs, especially networked logging (as in Field Day) and logging for digital mode programs.

## Remote Control

```{r}
#| echo: false
software_versions |>
  dplyr::filter(type == "remote") |>
  dplyr::select(station,software, version, date) |>
  dplyr::arrange(station) |>
  knitr::kable(format = "html") 
```

