---
title: "WSJT-X Operations on K3S"
author: "Rick Gilmore K3ROG"
date: "`r Sys.time()`"
output: html_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, 
                      message = FALSE,
                      fig.align = "center",
                      out.width = "600px")
```

### WSTJ-X on K3S/NARC2

#### On the PC

1. Open WSTJ-X (Icon is on desktop).

**Note**: If you will be using the rig regularly, you may wish to clone an existing Configuration set and edit it for your particular use. 
From the Configurations menu, choose a source Configuration, e.g., Standard Ops, select “Clone”, then from the Configurations menu, choose the clone, and switch to it by selecting the “Switch To” menu item. 
When WSTJ-X reopens with the new Configurations set, open Settings from File/Settings menu and confirm the settings.

2. Confirm settings

(It’s not essential to confirm the settings each time you start up, but doing so will make sure that you are able to operate without difficulty.)

Open Settings from File/Settings menu and confirm the settings.

*General tab:*

Set my Call to your personal callsign unless you have permission to use the club callsign (W3YA). 
Set any Display or Behavior settings per your personal preferences.

*Radio tab:*

Rig: Elecraft K3S</br>
CAT Control: COM3</br>
Baud Rate: 19200</br>
8 bits, 1 stop bit, none</br>

Force Control Lines: unset</br>
PTT method: CAT (port should be COM3)</br>
Mode: Data/pkt</br>
Split operation: Rig or Fake It</br>

*Audio tab:*
Input: USB Audio Codec</br>
Output: USB Audio Codec</br>

*Advanced tab*:

Check or uncheck Special Operating Activity per situation.

3. Check clock accuracy

Open browser, visit https://time.is

If you have a cellular hotspot, connect it to the HUB, power the HUB, wait for the computers to establish an internet connection, and allow the Meinberg time server to update the time

#### On K3S

1. Confirm rig is in Data A mode (if necessary, hit MODE button to cycle to data mode; indicator will be near Tx icon on right side of the display).

Press (and hold) the DATA MD button on the middle right of the panel.
Using the VFO B knob, select DATA A (not AFSK A).
Press DATA MD again to enter change.

2. Set bandwidth to maximum (4 kHz) by rotating WIDTH knob (above and to the left of the VFO A knob) clockwise until the screen shows a 4.0 bandwidth.

3. Set MIC SEL to LINE; set level to 30 (midrange)

4. Set ALC. 

From within WSTJ-X, hit Tune button; adjust audio level from computer “speaker” slider and WSTJ-X Power slider until ALC meter reads about 4 bars. Then adjust K3S mic gain to produce 4 bars solid with the 5th bar flickering.

Adjust transmit power via Power knob on K3S.
Remember, WSJT-X is a weak signal mode. 
Less than 50 W is plenty.
 
#### On KPA1500

<!-- Elecraft KPA1500 -->
```{r, child = 'WSJT-X-KPA1500.Rmd'}
```
